\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

% FORMAT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% MACROS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\titleformat{\section}{
  \vspace{-10pt}
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\newcommand{\cvItem}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2\\
    \textit{\small #3} & \textit{\small #4}
  \end{tabular*}
  \vspace{-5pt}
}

\newcommand{\cvSmallItem}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1:} #3 & #2\\
    \multicolumn{2}{l}{\small #4}
  \end{tabular*}
  \vspace{-5pt}
}

\newcommand{\cvSubitem}[1]{
  \item
  \small{#1}
  \vspace{-2pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\cvItemStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\cvItemEnd}{\end{itemize}}
\newcommand{\cvSubitemStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\cvSubitemEnd}{\end{itemize}\vspace{-5pt}}

% CV %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% TITLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
\textbf{\LARGE Sequoia Eyzaguirre}\\
sequoia@berkeley.edu $\vert$ sequoia-tree.github.io
\end{center}

% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\cvItemStart
\cvItem
{University of California, Berkeley}
{Berkeley, CA}
{B.A. of Computer Science with Highest Honors}
{August 2016 -- May 2019}
\cvSubitemStart
\cvSubitem{
$\Phi$BK Laureate, Regents' \& Chancellor's Scholar, EECS Honors Student, Outstanding Graduate Student Instructor.
}
\cvSubitem{
4.0 GPA, with an A+ in most of my upper-division / graduate EECS courses including CS 189: Machine Learning.
}
\cvSubitemEnd
\cvItemEnd

% RESEARCH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}

\cvItemStart
\cvItem
{Malasakit 2.0 (IEEE GHTC 2018)}
{Berkeley, CA}
{CITRIS \& the Banatao Institute}
{November 2017 -- October 2018}
\cvSubitemStart
\cvSubitem{
Introduces multidialectal voice recognition to improve accessibility for low-literacy regions. Deployed in 4 field tests.
}
\cvSubitemEnd
\cvItem
{Malasakit 1.0 (IEEE GHTC 2017)}
{Berkeley, CA}
{CITRIS \& the Banatao Institute}
{April 2017 -- October 2017}
\cvSubitemStart
\cvSubitem{
Robust to regional language differences unlike most supervised classification techniques, Malasakit identifies locally valuable disaster risk reduction (DRR) strategies and assesses correlations in related textual / demographic data.
}
\cvSubitem{
Deployed in 12 field tests across the Philippines to crowdsource and collaboratively filter 100's of DRR strategies.
}
\cvSubitem{
Won the Chancellor's Award for Research in the Public Interest.
}
\cvSubitem{
Runner-up for the Pacific Telecommunications Council's Best Quality of Life Improvement Award.
}
\cvSubitemEnd
\cvItem
{FORDS: A First-Order Driving Simulator}
{Berkeley, CA}
{UC Berkeley AUTOLab, Samsung}
{April 2017 -- December 2017}
\cvSubitemStart
\cvSubitem{
Released as an Open A.I. module developed for Samsung, to generate synthetic data for training self-driving agents.
}
\cvSubitem{
Laid groundwork for FLUIDS: A First-Order Local Urban Intersection Driving Simulator, published at CASE 2018.
}
\cvSubitemEnd
\cvItem
{Development on AvatarMind's iPal Robot}
{Berkeley, CA}
{UC Berkeley AUTOLab, AvatarMind}
{August 2016 -- May 2017}
\cvSubitemStart
\cvSubitem{
Implemented and benchmarked reliable actuation of poses from the Human3.6M dataset under stochastic controls.
}
\cvSubitem{
Accomplished real-time cleaning of noisy video data from a \$10 webcam to make it usable for human pose mimicry.
}
\cvSubitemEnd
\cvItemEnd

% TEACHING & COURSE DEVELOPMENT %%%%%%%%

\section{Teaching \& Course Development}

\cvItemStart
\cvItem
{CS 61A: The Structure and Interpretation of Computer Programs}
{Berkeley, CA}
{Head T.A. of Teaching, Head T.A. of Software, Guest Lecturer, T.A., Tutor}
{June 2017 -- December 2018}
\cvSubitemStart
\cvSubitem{
Wrote a popular beginner-level textbook covering novel approaches to thinking about recursion and DP.
}
\cvSubitem{
Invented a method of diagramming code execution, soon to be a standard component of the curriculum.
}
\cvSubitem{
Integrated MOSS with existing course infrastructure to detect plagiarism in programming assignments.
}
\cvSubitem{
Taught the highest-rated discussion and lab sections in the Spring 2018 and Fall 2018 semesters.
}
\cvSubitem{
Spearheaded a concept-oriented office hours program, averaging twice the turnout of normal office hours.
}
\cvSubitemEnd
\cvItem
{CS 370: Introduction to Teaching Computer Science}
{Berkeley, CA}
{Instructor of Record, Head T.A., Guest Lecturer, Content Developer}
{August 2017 -- December 2018}
\cvSubitemStart
\cvSubitem{
Single-handedly ran CS 370 for a year, scheduling nearly 10,000 hours of tutoring and training $\sim$250 new course staff.
}
\cvSubitem{
Taught in Summer `18 as the youngest ever instructor of record in the department. It was the top-rated class offered.
}
\cvSubitem{
Engaged faculty, who voted unanimously to accredit CS 370 for the pedagogy training required of all EECS T.A.'s.
}
\cvSubitem{
Scaled CS 370 to 4 times its size, enabling 5,750+ hours of tutoring per semester. Simultaneously oversaw a rise in enrollment to 17\% underrepresented minorities (compared to 2\% in the department), and from 17\% to 50\% female.
}
\cvSubitem{
Redesigned the entire curriculum -- including lesson plans, assignments, course infrastructure, and exams -- to communicate hands-on teaching advice, and also modern research on pedagogy and psychosocial factors in learning.
}
\cvSubitemEnd
\cvItem
{CS 186: Introduction to Database Systems}
{Berkeley, CA}
{T.A., Content Developer}
{January 2019 -- May 2019}
\cvSubitemStart
\cvSubitem{
Writing a new official textbook covering database architecture and novel approaches to writing / visualizing SQL.
}
\cvSubitemEnd
\cvItem
{Berkeley Institute of Data Science \& the Data Science Education Program}
{Berkeley, CA}
{Guest Lecturer, Content Developer}
{May 2017 -- May 2018}
\cvSubitemStart
\cvSubitem{
Redesigned the curriculum for Engineering 7, UC Berkeley's introductory programming course for mechanical engineers. The new curriculum, integrated with Jupyter and its own autograder, was well-received by faculty.
}
\cvSubitem{
Designed curricula for LS 88: Visualizing Data and Art 23: Data Arts, to engage psychology students in data science.
}
\cvSubitemEnd
\cvItemEnd

\newpage

% COMMUNITY SERVICE %%%%%%%%%%%%%%%%%%%%

\section{Community Service \& Diversity Initiatives}

\cvItemStart
\cvSmallItem
{Hunting Hunger Charity for the Homeless}
{Barstow, CA and Berkeley, CA}
{Founder \& Chair}
{Raised \$10,000+ and delivered 2,500+ meals to homeless CA residents and impoverished veterans of the U.S. Marines.}
\cvSmallItem
{Semper Fi Fund for Wounded Warriors}
{San Clemente, CA}
{Activist \& Donor}
{Wrote a book to raise awareness for military families, and donated all \$10,000+ profits to the Semper Fi Fund.}
\cvSmallItem
{CS Scholars \& CS Kickstart}
{Berkeley, CA}
{Head Student Instructor}
{Taught female and underrepresented EECS freshmen how to combat impostor syndrome, stereotype threat, etc.}
\cvSmallItem
{Hispanic Heritage Club}
{Barstow, CA}
{Founder \& President}
{Oversaw a 25\% decline in reports of racial prejudice against Hispanic students at Barstow Community College.}
\cvItemEnd

\end{document}
